Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-07 paper.tex
Add references and start interpreting regression.

We also calculate the characteristic path length for each WikiProject coeditor network.
The {\em distance} from editor A to editor B is the length of the shortest path from A to B.
The {\em characteristic path length} is the mean distance between all editor pairs.
If no path exists between two editors, we exclude that pair from the mean.
For brevity, we will simply refer to this quantity as the {\em path length}.
The path length represents how quickly information can move through the network.
Networks with longer paths require more interactions for information to propagate through
the network.

Our final network measure quantifies the connectivy of a project's coeditor network using
min-cut size.
The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
no path exists from $s$ to $t$.
The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
The size of the graph min-cut quantifies the connectivity of a graph,
but only incorporates information about edges lying on paths crossing the min-cut.
Instead, we use the mean size of all minimum $st$-cuts, which we refer to as the
{\em mean min-cut}.
This measure quantifies the number of redundant paths information can take through the network.
Networks with higher redundancy are more resilient to errors on one path \cite{}
and allow innovation to propagate through complex contagion,
in which innovations are only adopted after multiple exposures thorugh different sources
\cite{}.

@@

We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
Each WikiProject is taken as a single observation.
The models include each project's coeditor network properties as independent variables.
We also include several project-level variables to control for confounding factors.
Some variables are log-transformed to reduce heteroscedasticity.

@@

>>>>

We also calculate the characteristic path length for each WikiProject coeditor network.
The {\em distance} from editor A to editor B is the length of the shortest path from A to B.
The {\em characteristic path length} is the mean distance between all editor pairs.
If no path exists between two editors, we exclude that pair from the mean.
For brevity, we will simply refer to this quantity as the {\em path length}.
The path length represents how quickly information can move through the network.
Networks with longer paths require more interactions for information to propagate through
the network,
which has been shown to reduce efficiency in some settings
\cite{mason_propagation_2008,barkoczi_social_2016}.

Our final network measure quantifies the connectivy of a project's coeditor network using
min-cut size.
The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
no path exists from $s$ to $t$.
The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
The size of the graph min-cut quantifies the connectivity of a graph,
but only incorporates information about edges lying on paths crossing the min-cut.
Instead, we use the mean size of all minimum $st$-cuts, which we refer to as the
{\em mean min-cut}.
This measure quantifies the number of redundant paths information can take through the network.
Networks with higher redundancy are more resilient to errors on one path \cite{albert_error_2000}
and allow innovations to propagate through complex contagion,
in which innovations are only adopted after multiple exposures thorugh different sources
\cite{centola_complex_2007}.

The mean path and min-cut network measures are computationally intensive,
requiring distance and minimum $st$-cut calculations for each all node pairs.
For larger projects, these calculations are impractical.
When coeditor networks were large, we employed sampling to determine mean path length and mean
min-cut.
For mean path length, source nodes were sampled, and path length was calculated to all destination nodes
from each of these.
For min-cut, node pairs were sampled.
In both cases, stratification was used to ensure the same number of nodes were were sampled from each of
12 node degree quantiles.
We estimated the error due to sampling by determining true values for a medium-sized project,
and calculating error as a function of sample-size.
Sample sizes were chosen such that relative error was below 10\%.
Even with sampling, however, it was impractical to calculate these properties for the largest projects,
so we exclude them from the analysis.
To control for bias in project size, we include several size-related variables in our models.

@@

We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
Each WikiProject is taken as a single observation.
The models include each project's coeditor network properties as independent variables.
We also include several project-level variables to control for confounding factors.
The C-efficiency is included in the model for performance to control for the presence of articles
that are actively being improved.
Projects with lower efficiency will have more works-in-progress and could have an artifically low
performance without controlling for efficiency.
Some variables are log-transformed to reduce heteroscedasticity.

@@

The regression results are consistent whether in-degree or out-degree skewness is used,
although the out-degree models are slightly more significant when modelling efficiency.
